Table on stock change factors per clinate zone

### 2021-07-24 ResultNotebooks/investigate_SOCflows.Rmd
update results scripts

year  <- "y2010"
years <- c(paste0("y",as.numeric(substring("y2010",2))-1), year)

@@

grepSpaceTimeC    <- function(x){return(collapseNames(dimSums(x[,year,"c"],dim=1)))}
grepSpaceTime     <- function(x){return(collapseNames(dimSums(x[,year,],dim=1)))}

@@

ResidueInput      <- grepSpaceTimeC(Landuse[,2,"crop"]* CarbonResidues)

@@

ManureExcretedTot <- grepSpaceTimeC(dimSums(ManureExcreted[,,c("stubble_grazing","confinement")], dim=c(3.1,3.2)))
#ManureRecycledTot <- grepSpaceTimeC(dimSums(ManureRecycled, dim=3.1))
ManureInput       <- dimSums(grepSpaceTimeC(Landuse[,2,"crop"]* CarbonManure), dim=3.1)
ManureLossTot     <- ManureExcretedTot - ManureInput

@@

SOCIn             <- dimSums(CarbonInTot, dim=3)
SOCtransfer       <- CarbonToEff[,,"crop"] 
SOCPrev           <- dimSums(grepSpaceTime(setYears(
                       SoilCarbonOut[,1,"actualstate"][,,"crop"]*Landuse[,1,"crop"], year)), dim=3)
SOCLoss           <- SOCPrev - SOCtot[,,"crop"] + SOCtransfer + SOCIn

@@

write.csv(as.data.frame(TotalSOCBudget), paste0(outputdir,"TotalSOCBudget.csv"))

@@

```{r}

DecayCut          <- Decay
DecayCut[Decay>1] <- 1

### Carbon In
f1        <- param[,,"f1"]
f2_crop   <- param[,,"f2_ft"]
f2_natveg <- param[,,"f2_nt"]
f3        <- param[,,"f3"]

# f2 has to be updated with new test runs

MineralizeFracInput <- setCells(mbind(add_dimension(collapseNames(CarbonInput[,,"totalC",invert=TRUE][1,,"res"]), dim=3.1, add = "lu", nm = "crop"),
                                      add_dimension(collapseNames(CarbonInput[,,"totalC",invert=TRUE][1,,"res"]), dim=3.1, add = "lu", nm = "natveg")), "GLO")
MineralizeFracInput[,,"metabDOC"]        <- f1
MineralizeFracInput[,,"crop.strucDOC"]   <- f2_crop
MineralizeFracInput[,,"natveg.strucDOC"] <- f2_natveg
MineralizeFracInput[,,"ligninC"]         <- f3

input2lu <- as.data.frame(list(c("res", findset("kli"), "litfall"),
                            c(rep("crop",6), "natveg")), col.names=c("input","lu"))

CarbonInEff       <- collapseNames(dimSums(toolAggregate(CarbonInput[,"y2010",][,,"totalC",invert=TRUE], rel=input2lu, dim=3.1) *
                                            MineralizeFracInput[,"y2010",] * Landuse[,"y2010",], dim=c(1,3.2)))

CarbonInSource   <- collapseNames(dimSums(CarbonInput[,"y2010",][,,"totalC",invert=TRUE]  * 
                                            toolAggregate(MineralizeFracInput[,"y2010",] * Landuse[,"y2010",], rel=input2lu, from="lu", to="input", dim=3.1), dim=c(1,3.2)))

CarbonInRaw       <- collapseNames(dimSums(SoilCarbonOut[,"y2010","steadystate"]*DecayCut[,"y2010",]*Landuse[,"y2010",], dim=c(1,3.3)))

### Carbon Out

CarbonOutRaw      <- collapseNames(dimSums(SoilCarbonOut[,"y2010","interstate"]*DecayCut[,"y2010",]*Landuse[,"y2010",], dim=c(1,3.3)))
CarbonOutEff      <- CarbonOutRaw + CarbonInEff - CarbonInRaw

### SOC State

SOCstate <- dimSums(SoilCarbonOut[,c("y2009","y2010"),c("actualstate","interstate")]*Landuse[,c("y2009","y2010"),], dim=c(1,3.3))

>>>>

year  <- paste0("y",seq(1975,2010,5))
years <- sort(c(paste0("y",as.numeric(substring(year,2))-1), year))

@@

grepSpaceTimeC    <- function(x){return(collapseNames(dimSums(x["DEU",year,"c"],dim=1)))}
grepSpaceTime     <- function(x){return(collapseNames(dimSums(x["DEU",year,],dim=1)))}

@@

ResidueInput      <- grepSpaceTimeC(Landuse[,year,"crop"]* CarbonResidues)

@@

ManureExcretedTot <- grepSpaceTimeC(dimSums(ManureExcreted[,,c("stubble_grazing","confinement")], dim=c(3.1,3.2)))
#ManureRecycledTot <- grepSpaceTimeC(dimSums(ManureRecycled, dim=3.1))
ManureInput       <- dimSums(grepSpaceTimeC(Landuse[,year,"crop"]* CarbonManure), dim=3.1)
ManureLossTot     <- ManureExcretedTot - ManureInput

@@

SOCIn             <- dimSums(CarbonInTot, dim=3)
SOCtransfer       <- CarbonToEff[,,"crop"] 
SOCPrev           <- dimSums(grepSpaceTime(setYears(
                       SoilCarbonOut[,setdiff(years,year),"actualstate"][,,"crop"]*
                         Landuse[,setdiff(years,year),"crop"], year)), dim=3)
SOCLoss           <- SOCPrev - SOCtot[,,"crop"] + SOCtransfer + SOCIn

@@

write.csv(as.data.frame(TotalSOCBudget), paste0(outputdir,"DEUSOCBudget.csv"))
write.magpie(TotalSOCBudget, paste0(outputdir,"DEUSOCBudget.cs3"))
```

```{r}
# investigate high yields

temp_crops <- c("maiz","tece","potato","sugr_beet","rapeseed","others","foddr")

library(mrcommons)
setConfig(cachefolder  = "/home/kristine/mnt/rd3mod/inputdata/cache/rev16", forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(mappingfolder = "/home/kristine/mnt/rd3mod/inputdata/mappings/")

croparea <- calcOutput("Croparea", aggregate = FALSE)

print((grepSpaceTimeC(FAOmassbalance[,,temp_crops][,,"production"])))
print(grepSpaceTime(croparea[,,temp_crops]))
print((grepSpaceTimeC(FAOmassbalance[,,temp_crops][,,"production"]))/grepSpaceTime(croparea[,,temp_crops]))

@@

### 2021-07-24 ResultNotebooks/results_SOCmaps.Rmd
update results scripts

rev <- "rev19"
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")

@@

for(item in scenarios){
   dir.create(path=paste0("Data/",paste0(rev,item)))
   untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
   files=filesNeeded, exdir=paste0("Data/", paste0(rev,item)), extras="--keep-newer-files ")
}

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-42,0,10),
                     limits = c(-46,0),
                     breaks = c(0, -42, -43, -44, -45, -46),
                     minor_breaks = seq(-2,-42,-2)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -24, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

>>>>

rev <- "rev26"
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")

@@

# for(item in scenarios){
#    dir.create(path=paste0("Data/",paste0(rev,item)))
#    untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    files=filesNeeded, exdir=paste0("Data/", paste0(rev,item)), extras="--keep-newer-files ")
# }

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-32,0,10),
                     limits = c(-38,0),
                     breaks = c(0, -32, -33, -34, -35, -36, -37, -38),
                     minor_breaks = seq(-1,-29,-2)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -34, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

### 2021-07-24 ResultNotebooks/results_SOCscenario.Rmd
update results scripts

rev         <- "rev16"
scenarios   <- c("histManagement","constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  "constManagement2-1975", "constResrate-1975", "constYield-1975",
                 "Initial-natveg", "Initial-natveg_constManagement-1975", "Initial-natveg_constManagement2-1975", 
                 "LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 "LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

# filesNeeded  <- c("SoilCarbon.rds","Landuse.rds")
# setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
# 
# untar(paste0(getConfig("outputfolder"),"/", rev, "histManagement_h12_carbonbudget.tgz"),
#       exdir="Data/histManagement", extras="--keep-newer-files ")
# 
# for(item in scenarios){
#    untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    files=filesNeeded, exdir=paste0("Data/", item), extras="--keep-newer-files ")
# }

@@

CarbonInput  <- read.magpie(paste0("Data/histManagement/CarbonInput.rds"))
Landuse      <- read.magpie(paste0("Data/histManagement/Landuse.rds"))
glo_SOCInput <- collapseNames(dimSums(CarbonInput[,,"totalC"] * Landuse, dim=c(1)))/collapseNames(dimSums(Landuse, dim=c(1)))

ci2plot <- c('above-ground residues'="ag.crop",          
             'below-ground residues'="bg.crop",          
             'manure from monogastrics'="livst_chick.crop",
             'manure from monogastrics'="livst_egg.crop",
             'manure from monogastrics'="livst_pig.crop",
             'manure from ruminants'="livst_milk.crop",  
             'manure from ruminants'="livst_rum.crop",   
             'natural litterfall and fine roots'="litfall.natveg")

@@

manage_scen <-  c(histManagement   = "histManagement",
                  constTillage     = "constTillage-mixedtill", 
                  constManure      = "constManure-1975",
                  constResidues    = "constResidues-1975", 
                  constManagement  = "constManagement-1975")

@@

limits <- c(-30,-21)
breaks <- c(-22, -24,- 26, -28, -30)

@@

init_scen   <-  c(`histManagement.Initial-natveg`  = "Initial-natveg", 
                  `constManagement.Initial-natveg` = "Initial-natveg_constManagement-1975",
                  `histManagement.Initial-lu`      = "histManagement", 
                  `constManagement.Initial-lu`     = "constManagement-1975")

@@

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#785EF0","#FE6100","#FFB000")
input_cols  <- scen_cols[1:4]

limits <- c(-30,-10)
breaks <- c(-10, -15,- 20, -25, -30)

initSOCemis <- ggplot() + geom_path(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),]), 
                                    aes(x = Year, y = Value, group=interaction(Data1,Data2), linetype=Data1, color=Data2)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color    ="Initialization",
        linetype ="Management") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c(scen_cols)[1:2], labels = unique(gsub("(.*)\\.(.*)","\\2", names(init_scen)))) +
  scale_linetype_manual(values=c(1,2), labels=unique(gsub("(.*)\\.(.*)","\\1", names(init_scen)))) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

>>>>

rev         <- "rev26"
scenarios   <- c("rev26histManagement", "rev26constManagement", "rev26constManagement2", "rev26constManagement_constClimate", "rev26constManagement2_constClimate", "rev26constManure", "rev26constResidues", "rev26constResrate", "rev26constTillage", "rev26constYield", "rev26Initial-1901_constManagement", "rev26Initial-1901_constManagement2", "rev26Initial-1901", "rev26Initial-0_constManagement", "rev26Initial-0_constManagement2", "rev26Initial-0")

# filesNeeded  <- c("SoilCarbon.rds","Landuse.rds")
# setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
# 
# untar(paste0(getConfig("outputfolder"),"/", rev, "histManagement_h12_carbonbudget.tgz"),
#       exdir=paste0("Data/",rev,"histManagement"), extras="--keep-newer-files ")

# for(item in scenarios){
#    untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    files=filesNeeded, exdir=paste0("Data/", rev, item), extras="--keep-newer-files ")
# }

@@

CarbonInput  <- read.magpie(paste0("Data/rev26histManagement/CarbonInput.rds"))
Landuse      <- read.magpie(paste0("Data/rev26histManagement/Landuse.rds"))
glo_SOCInput <- collapseNames(dimSums(CarbonInput[,,"totalC"] * Landuse, dim=c(1)))/collapseNames(dimSums(Landuse, dim=c(1)))

ci2plot <- c('above-ground residues'="ag.crop",          
             'below-ground residues'="bg.crop",          
             'manure from monogastrics'="livst_chick.crop",
             'manure from monogastrics'="livst_egg.crop",
             'manure from monogastrics'="livst_pig.crop",
             'manure from ruminants'="livst_milk.crop",  
             'manure from ruminants'="livst_rum.crop",   
             'natural litterfall wood fraction'="wood.natveg",
             'natural litterfall leaf fraction'="leaf.natveg")

@@

manage_scen <-  c(histManagement   = "rev26histManagement",
                  constTillage     = "rev26constTillage", 
                  constManure      = "rev26constManure",
                  constResidues    = "rev26constResidues", 
                  constManagement  = "rev26constManagement")#,
                  #constManagementNoCC = "rev26constManagement_constClimate")

@@

limits <- c(-40,-32)
breaks <- c(-32, -34,- 36, -38, -40)

@@

init_scen   <-  c(`histManagement.Initial-natveg`          = "rev26Initial-1901", 
                  `constManagement.Initial-natveg`         = "rev26Initial-1901_constManagement",
                  `histManagement.Initial-eq`              = "rev26Initial-0", 
                  `constManagement.Initial-eq`             = "rev26Initial-0_constManagement",
                  `histManagement.Initial-spinup1530`      = "rev26histManagement", 
                  `constManagement.Initial-spinup1530`     = "rev26constManagement")

@@

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#648FFF","#785EF0","#DC267F")
input_cols  <- scen_cols[1:4]

limits <- c(-55,-25)
breaks <- c( -30,-40,-50 )

initSOCemis <- ggplot() + geom_path(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),]), 
                                    aes(x = Year, y = Value, group=interaction(Data1,Data2), linetype=Data1, color=Data2)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color    ="Initialization",
        linetype ="Management") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c(scen_cols)[1:3], labels = unique(gsub("(.*)\\.(.*)","\\2", names(init_scen)))) +
  scale_linetype_manual(values=c(1,2), labels=unique(gsub("(.*)\\.(.*)","\\1", names(init_scen)))) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

### 2021-07-24 ResultNotebooks/results_SOCtable.Rmd
update results scripts

scenarios <- c("rev19histManagement","rev18histManagement_ResAllom_2021_02_01")
outputdir <- "Output/"

@@

SoilCarbon <- read.magpie(paste0("Data/",scenarios[2],"/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/",scenarios[2],"/Landuse.rds"))
```

@@

years             <- findset("past")
climateIPCC       <- readRDS("Data/histManagement/IPCC_reduced.rds")

### calculating stock change factors
SOCDens           <- dimSums(SoilCarbon[,years,c("actualstate","naturalstate")], dim=3.3) 
SOCDens[,,"naturalstate.crop"] <- SOCDens[,,"actualstate.crop"]

CShare_ipcczone   <- dimSums(climateIPCC * SOCDens[,,"crop"][,,"actualstate"]   * Landuse[,years,"crop"], dim=1)/
                     dimSums(climateIPCC * SOCDens[,,"natveg"][,,"naturalstate"] * Landuse[,years,"crop"], dim=1)

@@

climateIPCCr       <- readRDS("Data/histManagement/IPCC_reduced.rds")
climateIPCC        <- readRDS("Data/histManagement/IPCC.rds")

@@

save_kable(save, file="Output/Images/TableSCF_comparison.png")
```

>>>>

scenarios <- c("rev26histManagement") #,"rev18histManagement_ResAllom_2021_02_01")
outputdir <- "Output/"

@@

SoilCarbon <- read.magpie(paste0("Data/",scenarios[1],"/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/",scenarios[1],"/Landuse.rds"))
```

@@

years             <- findset("past")
climateIPCCr      <- readRDS("Data/rev26histManagement/IPCC_reduced.rds")

### calculating stock change factors cropand weighted
SOCDens           <- dimSums(SoilCarbon[,years,c("actualstate","naturalstate")], dim=3.3) 
SOCDens[,,"naturalstate.crop"] <- SOCDens[,,"actualstate.crop"]

CShare_ipcczone   <- dimSums(climateIPCCr * SOCDens[,,"crop"][,,"actualstate"]   * Landuse[,years,"crop"], dim=1)/
                     dimSums(climateIPCCr * SOCDens[,,"natveg"][,,"naturalstate"] * Landuse[,years,"crop"], dim=1)

# CShare_ipcczone   <- dimSums(climateIPCCr * toolConditionalReplace(SOCDens[,,"crop"][,,"actualstate"]/SOCDens[,,"natveg"][,,"naturalstate"],
#                                                                  c("is.na()", "is.nan()", "is.infinite()",">3"), c(1,1,1,5)) * Landuse[,years,"crop"], dim=1)/
#                     dimSums(climateIPCCr * Landuse[,years,"crop"], dim=1)

@@

climateIPCCr       <- readRDS("Data/rev26histManagement/IPCC_reduced.rds")
climateIPCC        <- readRDS("Data/rev26histManagement/IPCC.rds")

@@

save_kable(save, file="Output/Images/TableSCF_comparison.png")
table
```
